\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-03 paper.tex
fixed compiler errors
put the names of other student authors first as they have significant contribution in case studies, this list is tentative anyway

\usepackage{color}
\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
\newcommand{\SCComment}[1]{\textcolor{orange}{Shuo: #1}}

@@

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^1$, Shuo Chen$^3$, Alastair F. Donaldson$^1$, John Erickson$^2$, Cheng Huang$^3$}\\
{\rm Akash Lal$^3$, Matt McCutchen$^4$, Shaz Qadeer$^3$, Wolfram Schulte$^2$, Paul Thomson$^1$}\\\\
$^1$Imperial College London, $^2$Microsoft, $^3$Microsoft Research\\
$^4$Massachusetts Institute of Technology\\
} % end author

@@

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism\SCComment{this paper mainly focuses on the nondet due to scheduling, right? There are other sources, e.g., arbitrary input, system call behavior, clock, random number, etc. I feel that "all sources" is perhaps an overclaim}. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem. \PDComment{we now have many bugs in Matt's system too.}

@@

\section{Distributed Systems \SCComment{change to "Distributed System Bugs"?}
\label{sec:bg}

>>>>

\usepackage{color}
\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
\newcommand{\SCComment}[1]{\textcolor{magenta}{Shuo: #1}}

@@

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$, Alastair F. Donaldson$^\dagger$}\\
{\rm John Erickson$^\ddagger$, Cheng Huang$^\star$, Akash Lal$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\ddagger$}\\\\
$^\dagger$Imperial College London, $^\ddagger$Microsoft, $^\star$Microsoft Research\\
$^\diamond$Massachusetts Institute of Technology\\
} % end author

@@

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism\SCComment{this paper mainly focuses on the nondet due to scheduling, right? There are other sources, e.g., arbitrary input, system call behavior, clock, random number, etc. I feel that ``all sources'' is perhaps an overclaim}. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem. \PDComment{we now have many bugs in Matt's system too.}

@@

\section{Distributed Systems \SCComment{change to "Distributed System Bugs"?}}
\label{sec:bg}
